MCLM parameters, interactive example

### 2024-05-20 apps/Graphical_representation_interactive.qmd
Drops redundant computation of `transf_matrix`

# Transform sample coordinates to orthonormal space:
observeEvent(
  list(transf_inv_transp(), lt_sample()),
  lt_sample_transf({

    # Compute actual (P) transform matrix (such that $P^TP = M = \Sigma^(-1)$):
    transf_matrix <- transf_inv_transp() |> t() |> solve()

    # Compute coordinates in transformed (i.e. orthonormal) space:
    lt_sample() |>
      rowid_to_column() |>
      pivot_longer(-rowid) |>
      group_by(rowid) |>
      mutate(value = transf_matrix %*% value |> drop()) |>
      pivot_wider()
  })
)

>>>>

# Transform sample coordinates to orthonormal space:
observeEvent(
  list(transf_matrix(), lt_sample()),
  lt_sample_transf({

    # Compute coordinates in transformed (i.e. orthonormal) space:
    lt_sample() |>
      rowid_to_column() |>
      pivot_longer(-rowid) |>
      group_by(rowid) |>
      mutate(value = transf_matrix() %*% value |> drop()) |>
      pivot_wider()
  })
)
